### 2013-07-22 doc/asplos14/tasks.tex
Use Inconsolata and fix up look and feel of listings.

\begin{figure}[htbp]
\begin{center}
\begin{scriptsize}
\begin{verbatim}
class node_t {
  key_t   key
  int64_t numChildren;
  GlobalAddress<node_t *> children;
};

void search(GlobalAddress<node_t *> node, key_t key) {
  // dereference is expected cache miss
  if (node->key == key) { 
    result = node;
    return;
  }
  parallel_for(0, node->numChildren, [=](int index) {
    // first dereference of children is expected cache miss
    search(node->children[index], key); 
  });
}
\end{verbatim}
\end{scriptsize}

>>>>

\begin{figure}[htbp]
\begin{center}
\begin{scriptsize}
\begin{lstlisting}[style=grappa]
class node_t {
  key_t   key
  int64_t numChildren;
  GlobalAddress<node_t> children;
};

void search(GlobalAddress<node_t> node, key_t key, GlobalAddress<node_t> result) {
  // deref of key is expected cache miss
  if (node->key == key) {
    delegate::write(result, node);
  } else {
    parallel_for(0, node->numChildren,
    [=](int index) {
      // first deref of children is likely miss
      search(node->children[index], key); 
    });
  }
}
\end{lstlisting}
\end{scriptsize}
